%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Fernando's Research Group, UIUC} % Job title
    {Undergraduate Researcher} % Organization
    {} % Location
    {Aug. 2025 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advised by \href{https://granha.github.io}{Prof. Fernando Granha Jeronimo}
        \item Studying asymptotic rate bounds of QLDPC codes
      \end{cvitems}
    }
    
 \vspace{3mm}
 
 \cventry
    {Illinois Mathematics Lab, UIUC} % Job title
    {Undergraduate Researcher} % Organization
    {} % Location
    {Jan. 2026 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advised by \href{https://publish.illinois.edu/mjunge/}{Prof. Marius Junge}
        \item Discovering new quantum games that separate classes of strategies
      \end{cvitems}
    }

 \vspace{3mm}

 \cventry
    {NCSA SPIN, UIUC} % Job title
    {Undergraduate Researcher} % Organization
    {} % Location
    {Feb. 2024 - May. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Created multi-GPU development pipeline for high-performance computing quantum simulations
        \item Recommended features for the Intel Quantum SDK that were added to development kid by Intel
      \end{cvitems}
    }

 \vspace{3mm}

 \cventry
    {Zhao Lab, Emory} % Job title
    {Student Researcher} % Organization
    {} % Location
    {Mar. 2021 - Dec. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advised by \href{https://cs.emory.edu/~lzhao41/}{Prof. Liang Zhao}
        \item Contributed to various graph machine learning works
      \end{cvitems}
    }
    
 \vspace{3mm}
 
 \cventry
    {EDIT AI, Dartmouth} % Job title
    {Student Researcher} % Organization
    {} % Location
    {Jun. 2021 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Advised by \href{https://cs.emory.edu/~lzhao41/}{Prof. Joshua Levy}
        \item Built ML models to improve nuclei detection for Mohs surgery
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
